### 2021-08-28 manuscript/introduction.tex
Correcoes nop pseudo algoritmo cgls.

In potential field methods, the properties of Toeplitz system have been used for downward continuation \citep{zhang-etal2016} and for 3D gravity-data inversion using a 2D multilayer model \citep{zhang-wong2015}. More recently in \cite{hogue2020tutorial} the authors provided an overview on modeling the gravity and magnetic kernels using the BTTB structures and \cite{renaut2020fast} used for inversion of both gravity and magnetic data to recover sparse subsurface structures.

>>>>

In potential field methods, the properties of Toeplitz system have been used for downward-continuation \citep{zhang-etal2016} and for 3D gravity-data inversion using a 2D multilayer model \citep{zhang-wong2015}. More recently in \cite{hogue2020tutorial} the authors provided an overview on modeling the gravity and magnetic kernels using the BTTB structures and \cite{renaut2020fast} used for inversion of both gravity and magnetic data to recover sparse subsurface structures.
